Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova Remnant

### 2014-12-03 manuscript/paper-tycho.tex
Merge VLA into data-tycho; new VLA/xray regions

We extract radio profiles from a $1.375 \unit{GHz}$ image of Tycho taken
with the VLA in A configuration in March 1994 (PI: D. Moffett); see
\citet{reynoso1997} for a detailed presentation.  The half-power beam width of
$\abt 1.5\arcsec$ just resolves thin radio rims and structure near the forward
shock; the image is sampled at $0.5\arcsec$.  We shift radio profiles forward
by $9\arcsec$ to correct for proper motion, assuming an $0.3\arcsec/\mt{yr}$
expansion rate \citep{katsuda2010-tycho}.  Figure~\ref{fig:radio-snr} shows the
extraction regions overlaying the radio image and the previous X-ray profile
regions of Figure~\ref{fig:snr}.

>>>>

We extract radio profiles from a $1.375 \unit{GHz}$ image of Tycho taken
with the VLA in A configuration in March 1994 (PI: D. Moffett); see
\citet{reynoso1997} for a detailed presentation.
\emph{Was data from all configurations merged?  Done by \citet{reynoso1997}.}
The half-power beam width of $\abt 1.5\arcsec$ just resolves thin radio rims
and structure near the forward shock; the image is sampled at $0.5\arcsec$.  We
shift radio profiles forward by $9\arcsec$ to correct for proper motion,
assuming an $0.3\arcsec/\mt{yr}$ expansion rate \citep{katsuda2010-tycho}.
Figure~\ref{fig:radio-snr} shows the extraction regions overlaying the radio
image and the previous X-ray profile regions of Figure~\ref{fig:snr}.
